---
title: "GROUP_PROJECT"
author: "JUSTIN_PATE"
date: "February 9, 2019"
output: word_document
---
goal for team.  The dataset is measurement data from actual airplane 3d measurements.
The field "MAG" is the deviation from nominal.  Nominal is the perfect location where magnitued would =0 in a perfect world/perfect airplane.

The goal for our team is to figure out correlation for each feature based on the field "SUB_GROUP" and which way each subgroup is trending by airplane number increase.  Are we getting better or worse?

The field SHIP, is the Airplane number meaning that each airplane number should have the same naumber of features.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
warning=FALSE
warnings=FALSE
library(splines)
 library(RcmdrMisc)
 library(car)
 library(carData)
 library(sandwich)
 library(effects)
library(graphics)
library(ggplot2)
library(scatterplot3d)
library(tidyr)
library(colorspace)


```

This data set is actual data taken from critical dimmensions on a commercial business jet.

```{r}
measuredata<- data.frame(read.csv(file="C:/School_SYR/TERM2/IST_687/PROJECT/SAMPLE_WING_CENTER_MEASURE_DATA.csv", header=TRUE, sep=","))
measuredata<-measuredata[,-1]
measuredata[1:10,]
subsetofmeasure<-measuredata[measuredata[,5]=="FLOOR FITTINGS",]
summary(subsetofmeasure)
hist(measuredata$MAG)

subsetofmeasure<-measuredata[measuredata[,5]=="PRESSURE WALL BL LH",]
summary(subsetofmeasure)
hist(subsetofmeasure$MAG)
#make a pie chart for measure breakdown
#with(measuredata, pie(table(SUB_GROUP), labels=levels(SUB_GROUP), xlab="", 
 # ylab="", main="SUB_GROUP", col=rainbow_hcl(28)))


```
MAKE A BOX PLOT
TEAM:  CAN YOU FIGURE OUT HOW TO TURN THE LABELS ON THE BOTTOM BY 90?
Also, how do I show all ships on the bottom

```{r}
library(ggplot2)
library(scatterplot3d)
library(tidyr)
boxplot(MAG~as.character(SHIP), data=measuredata,id=list(method="y"),axis.text.x=element_text(angle=90,hjust=2))

plotbyship<-ggplot(measuredata, aes(x=as.character(SHIP), y=MAG, group=1))+geom_line(color="red", linetype="dashed")+geom_point()+theme(text=element_text(size=8),axis.text.x=element_text(angle=90,hjust=2))
plotbyship
#scatterplot(MAG~SHIP | SUB_GROUP, regLine=FALSE, smooth=FALSE,boxplots=FALSE, by.groups=TRUE, data=measuredata)#HOW DO I GET RID OF THE COLOR WARNINGS?


```
MAKING DIFFERENT DATASETS FOR TEAM WITH sql AND SHOW BASIC SCATTER PLOTS

```{r}
library(sqldf)
avgmagdf<-sqldf("SELECT SHIP, SUB_GROUP, avg(mag) AS AVERAGEMAG FROM measuredata GROUP BY SUB_GROUP, SHIP")
avgmagdf[1:10,] #look at it
```
make a data set that shows range.  This represents how unstable the process is over time.  Process with larger ranges should be focused on more.
```{r}


rangeofmagdfBYSHIP<-sqldf("SELECT SHIP, SUB_GROUP, max(mag)-min(mag) AS rangeMAG FROM measuredata GROUP BY SHIP, SUB_GROUP ORDER BY max(mag)-min(mag) DESC")
rangeofmagdfBYSHIP[1:10,] #look at it

avgofranges<-sqldf("SELECT SUB_GROUP, avg(rangeMAG) AS avgofrangeMAG FROM rangeofmagdfBYSHIP GROUP BY SUB_GROUP ORDER BY avg(rangeMAG) DESC")
avgofranges[1:15,] #look at it


```

make a data set that shows in tolerance or out of tolerance binary.  This represents how unstable the process is over time.  Process with larger ranges should be focused on more.
```{r}
inoroutdf<-sqldf("SELECT SHIP, SUB_GROUP, min(case when mag <=maxtol and mag>=mintol then 1 else 0 end) AS passfail FROM measuredata GROUP BY SUB_GROUP, SHIP")
inoroutdf[1:10,] #look at it 1=pass and 0=faile

```

```{r}
Boxplot(MAG~SUB_GROUP, data=measuredata, id=list(method="y") + theme(text=element_text(size=8),axis.text.x=element_text(angle=90,hjust=2)))
```

```{r}

measuredata<-measuredata[,-1]
measuredata[1:10,]
#with(measuredata, Hist(MAG, groups=SUB_GROUP, scale="frequency", breaks="Sturges", col="darkgray"))
```

```{r}
#rangedf<-sqldf("SELECT SUB_GROUP, range(mag) AS range FROM measuredata GROUP BY SUB_GROUP")
#rangedf[1:10,] #look at it
```

```{r}
mdpivotbyfeature<- data.frame(read.csv(file="C:/School_SYR/TERM2/IST_687/PROJECT/lh_max_pivot.csv", header=TRUE, sep=","))
mdpivotbyfeature
g<-ggplot(mdpivotbyfeature, aes(x=FLOOR.SILLS.BL.LH+PRESSURE.WALL.BL.LH+STUB.FRAMES.WL.LH, y=FLOOR.SILLS.BL.LH)) + geom_point()
g+ stat_smooth(method="lm", col="red")
lmodeltest=lm(formula=STUB.FRAMES.BL.LH~FLOOR.SILLS.BL.LH+PRESSURE.WALL.BL.LH+STUB.FRAMES.WL.LH, data=mdpivotbyfeature)
summary(lmodeltest)


```


```{r}
g<-ggplot(mdpivotbyfeature, aes(x=FLOOR.SILL.WL.RH, y=PRESSURE.WALL.EOP.RH)) + geom_point()
g+ stat_smooth(method="lm", col="red")
lmodeltest=lm(formula=PRESSURE.WALL.EOP.RH~FLOOR.SILL.WL.RH, data=mdpivotbyfeature)
summary(lmodeltest)
mdpivotbyfeature[1:10,]
```

